The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2022-01-26 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd
Calculations for adjusted p-values

titles <- c(2020, "2017-19", "Z-test P-value", "Nonparametric P-value")
rows <- c("Home Win ", "Home Scoring", "Away Scoring", "Home 2P", "Home 3P",
          "Home FT", "Away 2P", "Away 3P", "Away FT")
results <- data.frame(rowone, rowtwo, rowthree, rowfour, rowfive, rowsix,
                    rowseven, roweight, rownine, stringsAsFactors = FALSE)
resultsfinal <- data.frame(t(results))
resultsfinal1 <- round(resultsfinal[1:2], 3)
resultsfinal2 <- round(resultsfinal[3:4], 4)
resultsfinal <-cbind(resultsfinal1, resultsfinal2)
colnames(resultsfinal) <- titles
row.names(resultsfinal) <- rows
```

>>>>

titles <- c(2020, "2017-19", "Z-test P-value", "Nonparametric P-value", "Adj P-value Z", "Adj P-value W")
rows <- c("Home Win ", "Home Scoring", "Away Scoring", "Home 2P", "Home 3P",
          "Home FT", "Away 2P", "Away 3P", "Away FT")
results <- data.frame(rowone, rowtwo, rowthree, rowfour, rowfive, rowsix,
                    rowseven, roweight, rownine, stringsAsFactors = FALSE)
resultsfinal <- data.frame(t(results))
resultsfinal1 <- round(resultsfinal[1:2], 3)
resultsfinal2 <- round(resultsfinal[3:4], 4)
resultsfinal3 <- round(resultsfinal[3:4]*9, 4)
resultsfinal <-cbind(resultsfinal1, resultsfinal2, resultsfinal3)
colnames(resultsfinal) <- titles
row.names(resultsfinal) <- rows
```
